Quantum Algorithms for Portflolio Optimisation and Option pricing

### 2024-06-05 project/paper-v2.tex
update project paper QAOA

In a similar fashion, the Quantum Approximate Optimisation Algorithm (QAOA) is another VQA that was first 
conceived as

\subsubsection{Quantum Amplitude Estimation}

>>>>

In a similar fashion, the Quantum Approximate Optimisation Algorithm (QAOA) is another VQA that was first 
proposed by Farhi et al. \cite{Farhi2014} for combinatorial optimisation problems (e.g. Max-Cut).

Mathematically, we can see the combinatorial optimisation problem as a graph with $m$ edges and $n$ vertices (see Fig. \ref{fig:combinatorial}). Then, define a binary string $x = \{x_1,\cdots, x_n\}$ with $x_i \in \{0, 1\}$. 
\begin{figure}[h!]
\centering 
\includegraphics[width=0.35\textwidth]{combinatorial-problem.pdf}
  \caption{\label{fig:combinatorial} A graph representation of a combinatorial optimisation problem with $n =4$ vertices and $m=6$ edges. Adapted from \cite{Baker2022}.} 
\end{figure}
The goal is to find the binary string that maximises the objective function: 
\begin{equation}
  \label{eq:14}
  C(x) = \sum_{i,j=1}^{n} \Sigma_{i,j} x_i (1-x_j)
\end{equation}

In Fig. \ref{fig:qaoa} we show the general structure of the QAOA. First, it initialise $n$ states as a uniform superposition
\begin{equation}
  \label{eq:15}
  |+\rangle^{\otimes n} = \frac{1}{\sqrt{2^n}} \sum_{x} |x\rangle 
\end{equation}
and then, it applies a sequence of $p$ anzates $U(\boldsymbol{\gamma}, \boldsymbol{\beta})$  that are defined as 
\begin{equation}
  \label{eq:16}
  U(\boldsymbol{\gamma}, \boldsymbol{\beta}) = \prod_{k=1}^{p} e^{-i\beta_k \mathcal{H}_M} e^{-i\gamma_k \mathcal{H}_C}
\end{equation}
where $\mathcal{H}_M$ and $\mathcal{H}_C$ are the mixing and cost Hamiltonians, respectively. The cost Hamiltonian $\mathcal{H}_C$ encodes the cost function of the problem and the mixing Hamiltonian helps guide the optimisation in Hilbert space towards ground state of $\mathcal{H}_C$ \cite{Moll2018}. Similar to the VQE, the cost Hamiltonian is defined by Eq. \ref{eq:10} and the mixer Hamiltonian 
is defined as $\mathcal{H}_M = -\sum_{i} \sigma_i^x$ \cite{Moll2018}.

After applying the anzates $p$ times, we measure the expectation value of the cost Hamiltonian $C(\boldsymbol{\gamma},\boldsymbol{\beta}) = \langle \psi(\boldsymbol{\gamma}, \boldsymbol{\beta})|\mathcal{H}_C|\psi(\boldsymbol{\gamma},\boldsymbol{\beta})\rangle$ and use a classical optimisation algorithm to update the parameters $\boldsymbol{\gamma}$ and $\boldsymbol{\beta}$ until we reach a minimum value of $C(\boldsymbol{\gamma},\boldsymbol{\beta})$.

\subsection{Quantum Amplitude Estimation}
